---
title: "EFN-BACK Behavioral Analyses"
output: html_notebook
---

```{r}

####### This script analyzes behavoiral data for EFN_BACK task
####### Created by Feng Gu in March 2019. Modified by Feng Gu in June 2020. 


########################################## SETTING UP ##############################################

rm(list = ls())

library(dplyr)
library(ggplot2)
library(viridis)
library(reshape2)
library(lme4)
library(lmerTest)

efn <- lapply(Sys.glob("~/Documents/CRANI/Active_Studies/CogRehab/Data/MRI_data/fMRI_behavioral_data/EFN_BACK/*/*.txt"), read.delim, stringsAsFactors=FALSE)

for (i in 1: length(efn)) {

efn[[i]]$PicList <- gsub("PicListNeg.", "Negative", efn[[i]]$PicList)
efn[[i]]$PicList <- gsub("PicListNeu.", "Neutral", efn[[i]]$PicList)
#use wildcard to rename PicList into two emotion conditions (negative vs. neutral) 

# accuracy rate overall 
efn[[i]]$acc_overall <- sum(efn[[i]]$Slide3.ACC == "1")/nrow(efn[[i]])

# accuracy rate one back
efn[[i]]$acc_ob <- sum(subset(efn[[i]], efn[[i]]$ListType == "1-Back")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$ListType == "1-Back"))

# accuracy rate two back
efn[[i]]$acc_tb <- sum(subset(efn[[i]], efn[[i]]$ListType == "2-Back")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$ListType == "2-Back"))

# accuracy rate negative
efn[[i]]$acc_neg <- sum(subset(efn[[i]], efn[[i]]$PicList == "Negative")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$PicList == "Negative"))

# accuracy rate neutral
efn[[i]]$acc_neu <- sum(subset(efn[[i]], efn[[i]]$PicList == "Neutral")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$PicList == "Neutral"))

# accuracy rate one back negative
efn[[i]]$acc_ob_neg <- sum(subset(efn[[i]], efn[[i]]$ListType == "1-Back" & efn[[i]]$PicList == "Negative")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$ListType == "1-Back" & efn[[i]]$PicList == "Negative"))

# accuracy rate one back neutral
efn[[i]]$acc_ob_neu <- sum(subset(efn[[i]], efn[[i]]$ListType == "1-Back" & efn[[i]]$PicList == "Neutral")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$ListType == "1-Back" & efn[[i]]$PicList == "Neutral"))

# accuracy rate two back negative
efn[[i]]$acc_tb_neg <- sum(subset(efn[[i]], efn[[i]]$ListType == "2-Back" & efn[[i]]$PicList == "Negative")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$ListType == "2-Back" & efn[[i]]$PicList == "Negative"))

# accuracy rate two back neutral
efn[[i]]$acc_tb_neu <- sum(subset(efn[[i]], efn[[i]]$ListType == "2-Back" & efn[[i]]$PicList == "Neutral")$Slide3.ACC == 1)/nrow(subset(efn[[i]], efn[[i]]$ListType == "2-Back" & efn[[i]]$PicList == "Neutral"))


# d' overall
efn[[i]]$hit_overall <- ifelse(efn[[i]]$LetterLevel == "Target" & efn[[i]]$Slide3.ACC == 1, 1, 0) #correct hit
efn[[i]]$fa_overall <- ifelse(efn[[i]]$LetterLevel == "Control" & efn[[i]]$Slide3.ACC == 0, 1, 0) #false alarm
efn[[i]]$miss_overall <- ifelse(efn[[i]]$LetterLevel == "Target" & efn[[i]]$Slide3.ACC == 0, 1, 0) #miss
efn[[i]]$cr_overall <- ifelse(efn[[i]]$LetterLevel == "Control" & efn[[i]]$Slide3.ACC == 1, 1, 0) #correct rejection

efn[[i]]$fa_rate_overall <- sum(efn[[i]]$fa_overall)/(sum(efn[[i]]$fa_overall)+sum(efn[[i]]$cr_overall)) #calculate false alarm rate
efn[[i]]$hit_rate_overall <- sum(efn[[i]]$hit_overall)/(sum(efn[[i]]$hit_overall)+sum(efn[[i]]$miss_overall)) #calculate hit rate  


efn[[i]]$fa_rate_overall <- ifelse(efn[[i]]$fa_rate_overall == "0", 1/nrow(efn[[i]]),
                             ifelse(efn[[i]]$fa_rate_overall == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$fa_rate_overall))

efn[[i]]$hit_rate_overall <- ifelse(efn[[i]]$hit_rate_overall == "0", 1/nrow(efn[[i]]),
                              ifelse(efn[[i]]$hit_rate_overall == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$hit_rate_overall))

efn[[i]]$dprime_overall <- -qnorm(efn[[i]]$fa_rate_overall)-(-qnorm(efn[[i]]$hit_rate_overall))


# d' one back
efn[[i]]$hit_ob <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "1-Back")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$ListType == "1-Back")$Slide3.ACC == 1, 1, 0) #correct hit
efn[[i]]$fa_ob <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "1-Back")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$ListType == "1-Back")$Slide3.ACC == 0, 1, 0) #false alarm
efn[[i]]$miss_ob <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "1-Back")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$ListType == "1-Back")$Slide3.ACC == 0, 1, 0) #miss
efn[[i]]$cr_ob <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "1-Back")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$ListType == "1-Back")$Slide3.ACC == 1, 1, 0) #correct rejection

efn[[i]]$fa_rate_ob <- sum(efn[[i]]$fa_ob)/(sum(efn[[i]]$fa_ob)+sum(efn[[i]]$cr_ob)) #calculate false alarm rate
efn[[i]]$hit_rate_ob <- sum(efn[[i]]$hit_ob)/(sum(efn[[i]]$hit_ob)+sum(efn[[i]]$miss_ob)) #calculate hit rate  


efn[[i]]$fa_rate_ob <- ifelse(efn[[i]]$fa_rate_ob == "0", 1/nrow(efn[[i]]),
                              ifelse(efn[[i]]$fa_rate_ob == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$fa_rate_ob))

efn[[i]]$hit_rate_ob <- ifelse(efn[[i]]$hit_rate_ob == "0", 1/nrow(efn[[i]]),
                               ifelse(efn[[i]]$hit_rate_ob == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$hit_rate_ob))

efn[[i]]$dprime_ob <- -qnorm(efn[[i]]$fa_rate_ob)-(-qnorm(efn[[i]]$hit_rate_ob))


# d' two back
efn[[i]]$hit_tb <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "2-Back")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$ListType == "2-Back")$Slide3.ACC == 1, 1, 0) #correct hit
efn[[i]]$fa_tb <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "2-Back")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$ListType == "2-Back")$Slide3.ACC == 0, 1, 0) #false alarm
efn[[i]]$miss_tb <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "2-Back")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$ListType == "2-Back")$Slide3.ACC == 0, 1, 0) #miss
efn[[i]]$cr_tb <- ifelse(subset(efn[[i]], efn[[i]]$ListType == "2-Back")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$ListType == "2-Back")$Slide3.ACC == 1, 1, 0) #correct rejection

efn[[i]]$fa_rate_tb <- sum(efn[[i]]$fa_tb)/(sum(efn[[i]]$fa_tb)+sum(efn[[i]]$cr_tb)) #calculate false alarm rate
efn[[i]]$hit_rate_tb <- sum(efn[[i]]$hit_tb)/(sum(efn[[i]]$hit_tb)+sum(efn[[i]]$miss_tb)) #calculate hit rate  


efn[[i]]$fa_rate_tb <- ifelse(efn[[i]]$fa_rate_tb == "0", 1/nrow(efn[[i]]),
                         ifelse(efn[[i]]$fa_rate_tb == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$fa_rate_tb))

efn[[i]]$hit_rate_tb <- ifelse(efn[[i]]$hit_rate_tb == "0", 1/nrow(efn[[i]]),
                          ifelse(efn[[i]]$hit_rate_tb == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$hit_rate_tb))

efn[[i]]$dprime_tb <- -qnorm(efn[[i]]$fa_rate_tb)-(-qnorm(efn[[i]]$hit_rate_tb))


# d' negative
efn[[i]]$hit_neg <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Negative")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$PicList == "Negative")$Slide3.ACC == 1, 1, 0) #correct hit
efn[[i]]$fa_neg <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Negative")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$PicList == "Negative")$Slide3.ACC == 0, 1, 0) #false alarm
efn[[i]]$miss_neg <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Negative")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$PicList == "Negative")$Slide3.ACC == 0, 1, 0) #miss
efn[[i]]$cr_neg <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Negative")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$PicList == "Negative")$Slide3.ACC == 1, 1, 0) #correct rejection

efn[[i]]$fa_rate_neg <- sum(efn[[i]]$fa_neg)/(sum(efn[[i]]$fa_neg)+sum(efn[[i]]$cr_neg)) #calculate false alarm rate
efn[[i]]$hit_rate_neg <- sum(efn[[i]]$hit_neg)/(sum(efn[[i]]$hit_neg)+sum(efn[[i]]$miss_neg)) #calculate hit rate  


efn[[i]]$fa_rate_neg <- ifelse(efn[[i]]$fa_rate_neg == "0", 1/nrow(efn[[i]]),
                         ifelse(efn[[i]]$fa_rate_neg == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$fa_rate_neg))

efn[[i]]$hit_rate_neg <- ifelse(efn[[i]]$hit_rate_neg == "0", 1/nrow(efn[[i]]),
                          ifelse(efn[[i]]$hit_rate_neg == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$hit_rate_neg))

efn[[i]]$dprime_neg <- -qnorm(efn[[i]]$fa_rate_neg)-(-qnorm(efn[[i]]$hit_rate_neg))


# d' neutral 
efn[[i]]$hit_neu <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Neutral")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$PicList == "Neutral")$Slide3.ACC == 1, 1, 0) #correct hit
efn[[i]]$fa_neu <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Neutral")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$PicList == "Neutral")$Slide3.ACC == 0, 1, 0) #false alarm
efn[[i]]$miss_neu <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Neutral")$LetterLevel == "Target" & subset(efn[[i]], efn[[i]]$PicList == "Neutral")$Slide3.ACC == 0, 1, 0) #miss
efn[[i]]$cr_neu <- ifelse(subset(efn[[i]], efn[[i]]$PicList == "Neutral")$LetterLevel == "Control" & subset(efn[[i]], efn[[i]]$PicList == "Neutral")$Slide3.ACC == 1, 1, 0) #correct rejection

efn[[i]]$fa_rate_neu <- sum(efn[[i]]$fa_neu)/(sum(efn[[i]]$fa_neu)+sum(efn[[i]]$cr_neu)) #calculate false alarm rate
efn[[i]]$hit_rate_neu <- sum(efn[[i]]$hit_neu)/(sum(efn[[i]]$hit_neu)+sum(efn[[i]]$miss_neu)) #calculate hit rate  


efn[[i]]$fa_rate_neu <- ifelse(efn[[i]]$fa_rate_neu == "0", 1/nrow(efn[[i]]),
                          ifelse(efn[[i]]$fa_rate_neu == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$fa_rate_neu))

efn[[i]]$hit_rate_neu <- ifelse(efn[[i]]$hit_rate_neu == "0", 1/nrow(efn[[i]]),
                           ifelse(efn[[i]]$hit_rate_neu == "1", (nrow(efn[[i]])-1)/nrow(efn[[i]]), efn[[i]]$hit_rate_neu))

efn[[i]]$dprime_neu <- -qnorm(efn[[i]]$fa_rate_neu)-(-qnorm(efn[[i]]$hit_rate_neu))



# RT overall 
efn[[i]]$RT_overall <- mean(efn[[i]]$Slide3.RT)

# RT one back 
efn[[i]]$RT_ob <- mean(subset(efn[[i]], efn[[i]]$ListType == "1-Back")$Slide3.RT)

# RT two back 
efn[[i]]$RT_tb <- mean(subset(efn[[i]], efn[[i]]$ListType == "2-Back")$Slide3.RT)

# RT negative 
efn[[i]]$RT_neg <- mean(subset(efn[[i]], efn[[i]]$PicList== "Negative")$Slide3.RT)

# RT neutral
efn[[i]]$RT_neu <- mean(subset(efn[[i]], efn[[i]]$PicList== "Neutral")$Slide3.RT)

# RT one back negative
efn[[i]]$RT_ob_neg <- mean(subset(efn[[i]], efn[[i]]$ListType == "1-Back" & efn[[i]]$PicList == "Negative")$Slide3.RT)

# RT one back neutral 
efn[[i]]$RT_ob_neu <- mean(subset(efn[[i]], efn[[i]]$ListType == "1-Back" & efn[[i]]$PicList == "Neutral")$Slide3.RT)

# RT two back negative
efn[[i]]$RT_tb_neg <- mean(subset(efn[[i]], efn[[i]]$ListType == "2-Back" & efn[[i]]$PicList == "Negative")$Slide3.RT)

# RT two back neutral 
efn[[i]]$RT_tb_neu <- mean(subset(efn[[i]], efn[[i]]$ListType == "2-Back" & efn[[i]]$PicList == "Neutral")$Slide3.RT)


}

efn <- bind_rows(efn)

attach(efn)
efn <- data.frame(Subject, Session, acc_overall, acc_ob, acc_tb, acc_neg, acc_neu, acc_ob_neg, acc_ob_neu, acc_tb_neg, acc_tb_neu, dprime_overall, dprime_ob, dprime_tb, dprime_neg, dprime_neu, RT_overall, RT_ob, RT_tb, RT_neg, RT_neu, RT_ob_neg, RT_ob_neu, RT_tb_neg, RT_tb_neu)
detach(efn)


efn$Subject <- sprintf("%03d", efn$Subject)
efn$Subject <- paste("CR", efn$Subject)
efn$Subject <- gsub(" ", "", efn$Subject)



subjects <- as.list(which(efn$Subject != lag(efn$Subject)))
for (i in 1:length(subjects)) {
  efn[subjects[[i]],"flag"] <- "flag"
}

efn[1, "flag"] <- "flag"
efn <- subset(efn, efn$flag == "flag")
efn$flag <- NULL


efn$Diagnosis <- ifelse(substr(efn$Subject, 3, 3) == "0", "HC",
                 ifelse(substr(efn$Subject, 3, 3) == "1", "SZ", "MDD"))

```


<br>
<br>
<br>
<br>

***
<center><font size="6"> <span style="color:#85c1e9"> **Accuracy Analysis** </span> </font> </center>
###*<span style="color: #ec7063"> Linear mixed model for rate of accuracy with subject ID as a random factor (other fixed covariates: cognitive load, emotion type, diagnosis, and three-way interaction among them) </span>*

```{r}

################################# ACCURACY RATE ################################

efn_acc <- melt(efn, id.vars = c("Subject", "Diagnosis"), measure.vars = c("acc_ob", "acc_tb", "acc_neu", "acc_neg"))
efn_acc$aspect <- ifelse(efn_acc$variable == "acc_ob" | efn_acc$variable == "acc_tb", "Cognitive Load", "Emotion")


efn_acc2 <- melt(efn, id.vars = c("Subject", "Diagnosis"), measure.vars = c("acc_ob_neu", "acc_ob_neg", "acc_tb_neu", "acc_tb_neg"))
efn_acc2$load <- ifelse(substr(efn_acc2$variable, 5, 6) == "ob", "1-back", "2-back")
efn_acc2$emotion <- ifelse(substr(efn_acc2$variable, 8, 10) == "neu", "Neutral", "Negative")
efn_acc2$emotion <- factor(efn_acc2$emotion, levels = c("Neutral", "Negative"))


model_acc <- lmer(value ~ load + emotion + Diagnosis + load*emotion*Diagnosis + (1|Subject), efn_acc2)
summary(model_acc)



acc <- ggplot(efn_acc, aes(y=value, x=Diagnosis)) +
  geom_point(aes(colour=variable), position=position_jitter(w=.3, h=.001), alpha=.3, size = 3) +
  geom_boxplot(aes(colour=variable), width=.5, alpha=.5, outlier.shape=NA)  +
  facet_grid(. ~ aspect) +
  scale_colour_viridis_d(
    begin=.1,end=.9,     
    na.translate=FALSE,  # use this command so "NA" values in the data don't get their own colour
    labels=c("1-back","2-back", "Neutral Emotion", "Negative Emotion")) +
  scale_y_continuous(name="Rate of Accuracy") +
  theme(panel.background = element_rect(fill = "white"), panel.border = element_rect(fill = NA, colour = "black"),
        axis.text = element_text(size = 20), axis.title=element_text(face = "bold", size=20)) +
  theme(strip.text.x = element_text(size = 18)) +
  theme(axis.title.y = element_text(face = "bold", size=25, margin=margin(r=10))) +
  theme(axis.title.x = element_text(face = "bold", size=25, margin=margin(t=15))) +
  theme(legend.title = element_blank(),
        legend.text = element_text(size = 20))



acc2 <- ggplot(efn_acc2, aes(y=value, x=Diagnosis)) +
  geom_point(aes(colour=variable), position=position_jitter(w=.3, h=.001), alpha=.3, size = 3) +
  geom_boxplot(aes(colour=variable), width=.5, alpha=.5, outlier.shape=NA)  +
  facet_grid(emotion ~ load) +
  scale_colour_viridis_d(
    begin=.1,end=.9,     
    na.translate=FALSE) +# use this command so "NA" values in the data don't get their own colour
  scale_y_continuous(name="Rate of Accuracy") +
  theme(panel.background = element_rect(fill = "white"), panel.border = element_rect(fill = NA, colour = "black"),
        axis.text = element_text(size = 20), axis.title=element_text(face = "bold", size=20)) +
  theme(strip.text.x = element_text(size = 18)) +
  theme(strip.text.y = element_text(size = 18)) +
  theme(axis.title.y = element_text(face = "bold", size=25, margin=margin(r=10))) +
  theme(axis.title.x = element_text(face = "bold", size=25, margin=margin(t=15))) +
  theme(legend.position = "none")

```

<br>
<br>

###*<span style="color:#ec7063"> Figures for Accuracy Rates </span>*

```{r fig1, fig.height=10, fig.width=15, fig.align="center"}
acc
```


```{r fig2, fig.height=10, fig.width=15, fig.align="center"}
acc2
```



<br>
<br>
<br>
<br>

***
<center><font size="6"> <span style="color:#85c1e9"> **d'** </span> </font> </center>
###*<span style="color: #ec7063"> Figure for d' </span>*

```{r}
############################## d' ###################################
efn_dprime <- melt(efn, id.vars = c("Subject", "Diagnosis"), measure.vars = c("dprime_ob", "dprime_tb", "dprime_neu", "dprime_neg"))
efn_dprime$aspect <- ifelse(efn_dprime$variable == "dprime_ob" | efn_dprime$variable == "dprime_tb", "Cognitive Load", "Emotion")


dprime <- ggplot(efn_dprime, aes(y=value, x=Diagnosis)) +
  geom_point(aes(colour=variable), position=position_jitter(w=.3, h=.001), alpha=.3, size = 3) +
  geom_boxplot(aes(colour=variable), width=.5, alpha=.5, outlier.shape=NA)  +
  facet_grid(. ~ aspect) +
  scale_colour_viridis_d(
    begin=.1,end=.9,     
    na.translate=FALSE,  # use this command so "NA" values in the data don't get their own colour
    labels=c("1-back","2-back", "Neutral Emotion", "Negative Emotion")) +
  scale_y_continuous(name="d'") +
  theme(panel.background = element_rect(fill = "white"), panel.border = element_rect(fill = NA, colour = "black"),
        axis.text = element_text(size = 20), axis.title=element_text(face = "bold", size=20)) +
  theme(strip.text.x = element_text(size = 18)) +
  theme(axis.title.y = element_text(face = "bold", size=25, margin=margin(r=10))) +
  theme(axis.title.x = element_text(face = "bold", size=25, margin=margin(t=15))) +
  theme(legend.title = element_blank(),
        legend.text = element_text(size = 20))

```

```{r fig3, fig.height=10, fig.width=15, fig.align="center"}
dprime
```




<br>
<br>
<br>
<br>

***
<center><font size="6"><span style="color:#85c1e9"> **RT Analysis** </span></font></center>
###*<span style="color: #ec7063"> Linear mixed model for RT with subject ID as a random factor (other fixed covariates: cognitive load, emotion type, diagnosis, and three-way interaction among them) </span>*

```{r}

############################# RT #####################################

efn_RT <- melt(efn, id.vars = c("Subject", "Diagnosis"), measure.vars = c("RT_ob", "RT_tb", "RT_neu", "RT_neg"))
efn_RT$aspect <- ifelse(efn_RT$variable == "RT_ob" | efn_RT$variable == "RT_tb", "Cognitive Load", "Emotion")


efn_RT2 <- melt(efn, id.vars = c("Subject", "Diagnosis"), measure.vars = c("RT_ob_neu", "RT_ob_neg", "RT_tb_neu", "RT_tb_neg"))
efn_RT2$load <- ifelse(substr(efn_RT2$variable, 4, 5) == "ob", "1-back", "2-back")
efn_RT2$emotion <- ifelse(substr(efn_RT2$variable, 7, 9) == "neu", "Neutral", "Negative")
efn_RT2$emotion <- factor(efn_RT2$emotion, levels = c("Neutral", "Negative"))


model_RT <- lmer(value ~ load + emotion + Diagnosis + load*emotion*Diagnosis + (1|Subject), efn_RT2)
summary(model_RT)


RT <- ggplot(efn_RT, aes(y=value, x=Diagnosis)) +
  geom_point(aes(colour=variable), position=position_jitter(w=.3, h=.001), alpha=.3, size = 3) +
  geom_boxplot(aes(colour=variable), width=.5, alpha=.5, outlier.shape=NA)  +
  facet_grid(. ~ aspect) +
  scale_colour_viridis_d(
    begin=.1,end=.9,     
    na.translate=FALSE,  # use this command so "NA" values in the data don't get their own colour
    labels=c("1-back","2-back", "Neutral Emotion", "Negative Emotion")) +
  scale_y_continuous(name="RT") +
  theme(panel.background = element_rect(fill = "white"), panel.border = element_rect(fill = NA, colour = "black"),
        axis.text = element_text(size = 20), axis.title=element_text(face = "bold", size=20)) +
  theme(strip.text.x = element_text(size = 18)) +
  theme(axis.title.y = element_text(face = "bold", size=25, margin=margin(r=10))) +
  theme(axis.title.x = element_text(face = "bold", size=25, margin=margin(t=15))) +
  theme(legend.title = element_blank(),
        legend.text = element_text(size = 20))



RT2 <- ggplot(efn_RT2, aes(y=value, x=Diagnosis)) +
  geom_point(aes(colour=variable), position=position_jitter(w=.3, h=.001), alpha=.3, size = 3) +
  geom_boxplot(aes(colour=variable), width=.5, alpha=.5, outlier.shape=NA)  +
  facet_grid(emotion ~ load) +
  scale_colour_viridis_d(
    begin=.1,end=.9,     
    na.translate=FALSE) +# use this command so "NA" values in the data don't get their own colour
  scale_y_continuous(name="RT") +
  theme(panel.background = element_rect(fill = "white"), panel.border = element_rect(fill = NA, colour = "black"),
        axis.text = element_text(size = 20), axis.title=element_text(face = "bold", size=20)) +
  theme(strip.text.x = element_text(size = 18)) +
  theme(strip.text.y = element_text(size = 18)) +
  theme(axis.title.y = element_text(face = "bold", size=25, margin=margin(r=10))) +
  theme(axis.title.x = element_text(face = "bold", size=25, margin=margin(t=15))) +
  theme(legend.position = "none")

```

<br>
<br>

###*<span style="color: #ec7063"> Figures for RT </span>*

```{r fig4, fig.height=10, fig.width=15, fig.align="center"}
RT
```

```{r fig5, fig.height=10, fig.width=15, fig.align="center"}
RT2
```